Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-05-12 paper.qmd
Updated Projection

```{r}
#| label: five-gau-tsne-projs
projection <- cbind(
  c(0.07108,0.19751,-0.21229,0.26341),
  c(-0.23494,0.27965,-0.01430,-0.15782))

@@

```{r}
#| label: five-gau-umap-projs
projection <- cbind(
  c(0.07108,0.19751,-0.21229,0.26341),
  c(-0.23494,0.27965,-0.01430,-0.15782))

@@

```{r}
#| label: five-gau-pacmap-projs
## First projection
projection <- cbind(
  c(0.07108,0.19751,-0.21229,0.26341),
  c(-0.23494,0.27965,-0.01430,-0.15782))

>>>>

```{r}
#| label: five-gau-tsne-projs
projection <- cbind(
  c(0.00660,-0.34942,0.14548,-0.12289),
  c(-0.18758,0.15398,0.30233,-0.08999))

@@

```{r}
#| label: five-gau-umap-projs
projection <- cbind(
  c(0.00660,-0.34942,0.14548,-0.12289),
  c(-0.18758,0.15398,0.30233,-0.08999))

@@

```{r}
#| label: five-gau-pacmap-projs
## First projection
projection <- cbind(
  c(0.00660,-0.34942,0.14548,-0.12289),
  c(-0.18758,0.15398,0.30233,-0.08999))
